---
title: "P8105 HW6"
author: "Wenbo Fei"
date: "12/9/2020"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(MASS)             
library(modelr)
library(purrr)
library(patchwork)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
theme_set(theme_minimal() + theme(legend.position = "bottom"))
```

# Problem 1

Data importing and cleaning
```{r Q1data, warning = FALSE, message=FALSE}
homicide_df = 
  read_csv("data/homicide-data.csv", na = c("", "NA", "Unknown")) %>% 
  mutate(
    city_state = str_c(city, state, sep = ", "),
    victim_age = as.numeric(victim_age),
    resolution = case_when(
      disposition == "Closed without arrest" ~ 0,
      disposition == "Open/No arrest"        ~ 0,
      disposition == "Closed by arrest"      ~ 1)
  ) %>% 
  filter(
    victim_race %in% c("White", "Black"),
    city_state != "Tulsa, AL") %>% 
  dplyr::select(city_state, resolution, victim_age, victim_race, victim_sex)
```

For the city of Baltimore, MD
```{r P1Q1}
baltimore_df =
  homicide_df %>% 
  filter(city_state == "Baltimore, MD")

glm(resolution ~ victim_age + victim_race + victim_sex, 
    data = baltimore_df,
    family = binomial()) %>% 
  broom::tidy() %>% 
  mutate(
    OR = exp(estimate),
    CI_lower = exp(estimate - 1.96 * std.error),
    CI_upper = exp(estimate + 1.96 * std.error)
  ) %>% 
  dplyr::select(term, OR, starts_with("CI")) %>% 
  knitr::kable(digits = 3)
```


For all cities
```{r P1Q2}
all_df = 
  homicide_df %>% 
  nest(data = -city_state) %>% 
  mutate(
    models = 
      map(.x = data, ~glm(resolution ~ victim_age + victim_race + victim_sex, data = .x, family = binomial())),
    results = map(models, broom::tidy)
  ) %>% 
  dplyr::select(city_state, results) %>% 
  unnest(results) %>% 
  mutate(
    OR = exp(estimate),
    CI_lower = exp(estimate - 1.96 * std.error),
    CI_upper = exp(estimate + 1.96 * std.error)
  ) %>% 
  dplyr::select(city_state, term, OR, starts_with("CI")) 
```

Create a plot to show the estimated ORs and CIs for each city. 
```{r P1plot}
all_df %>% 
  filter(term == "victim_sexMale") %>% 
  mutate(city_state = fct_reorder(city_state, OR)) %>% 
  ggplot(aes(x = city_state, y = OR)) + 
  geom_point() + 
  geom_errorbar(aes(ymin = CI_lower, ymax = CI_upper)) + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1))

```

# Problem 2
```{r P2data, message=FALSE, warning=FALSE}
baby_df = 
  read_csv("data/birthweight.csv") %>% 
  janitor::clean_names() %>%
  mutate(
    babysex = factor(babysex), 
    frace = factor(frace), 
    malform = factor(malform), 
    mrace = factor(mrace)
    )
# check for missing data
baby_df %>%  summarise(na_count = sum(is.na(.))) #no missing value
```

Propose a regression model for birthweight. 

Do step-wise model selection based on AIC.
```{r P2model}
# step-wise model selection based on AIC
step_model = lm(bwt ~ ., data = baby_df) %>%
  stepAIC(direction = "both", trace = F) %>% 
  broom::tidy()

step_model
```

Based on the result, the proposed model is: $bwt = \beta_0 + \beta_1* babysex2 + \beta_2*bhead + \beta_3*blength + \beta_4*delwt + \beta_5*fincome + \beta_6*gaweeks + \beta_7*mheight + \beta_8*mrace2 + \beta_9*mrace3 + \beta_{10}*mrace4  + \beta_{11}*parity + \beta_{12}*ppwt + \beta_{13}*smoken$

Show a plot of model residuals against fitted values
```{r P2plot}
#proposed model
baby_fit = lm(bwt ~ babysex + bhead + blength + delwt + fincome + gaweeks + mheight + mrace + parity + ppwt + smoken, data = baby_df)
#plot  
baby_df %>% 
  add_predictions(baby_fit) %>% 
  add_residuals(baby_fit) %>% 
  ggplot(aes(y = resid, x = pred)) + 
  geom_point(alpha = .2) + 
  labs(
    title = "Plot of model residuals vs. fitted values",
    x = "Fitted Values",
    y = "Residuals"
  )
```



