---
title: "P8105 HW6"
author: "Wenbo Fei"
date: "12/9/2020"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(MASS)             
library(modelr)
library(purrr)
library(patchwork)

knitr::opts_chunk$set(
	echo = TRUE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
theme_set(theme_minimal() + theme(legend.position = "bottom"))
```

# Problem 1

Data importing and cleaning
```{r Q1data, warning = FALSE, message=FALSE}
homicide_df = 
  read_csv("data/homicide-data.csv", na = c("", "NA", "Unknown")) %>% 
  mutate(
    city_state = str_c(city, state, sep = ", "),
    victim_age = as.numeric(victim_age),
    resolution = case_when(
      disposition == "Closed without arrest" ~ 0,
      disposition == "Open/No arrest"        ~ 0,
      disposition == "Closed by arrest"      ~ 1)
  ) %>% 
  filter(
    victim_race %in% c("White", "Black"),
    city_state != "Tulsa, AL") %>% 
  dplyr::select(city_state, resolution, victim_age, victim_race, victim_sex)
```

For the city of Baltimore, MD
```{r P1Q1}
baltimore_df =
  homicide_df %>% 
  filter(city_state == "Baltimore, MD")

glm(resolution ~ victim_age + victim_race + victim_sex, 
    data = baltimore_df,
    family = binomial()) %>% 
  broom::tidy() %>% 
  mutate(
    OR = exp(estimate),
    CI_lower = exp(estimate - 1.96 * std.error),
    CI_upper = exp(estimate + 1.96 * std.error)
  ) %>% 
  dplyr::select(term, OR, starts_with("CI")) %>% 
  knitr::kable(digits = 3)
```


For all cities
```{r P1Q2}
all_df = 
  homicide_df %>% 
  nest(data = -city_state) %>% 
  mutate(
    models = 
      map(.x = data, ~glm(resolution ~ victim_age + victim_race + victim_sex, data = .x, family = binomial())),
    results = map(models, broom::tidy)
  ) %>% 
  dplyr::select(city_state, results) %>% 
  unnest(results) %>% 
  mutate(
    OR = exp(estimate),
    CI_lower = exp(estimate - 1.96 * std.error),
    CI_upper = exp(estimate + 1.96 * std.error)
  ) %>% 
  dplyr::select(city_state, term, OR, starts_with("CI")) 
```

Create a plot to show the estimated ORs and CIs for each city. 
```{r P1plot}
all_df %>% 
  filter(term == "victim_sexMale") %>% 
  mutate(city_state = fct_reorder(city_state, OR)) %>% 
  ggplot(aes(x = city_state, y = OR)) + 
  geom_point() + 
  geom_errorbar(aes(ymin = CI_lower, ymax = CI_upper)) + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1))

```

# Problem 2
```{r P2data, message=FALSE, warning=FALSE}
baby_df = 
  read_csv("data/birthweight.csv") %>% 
  janitor::clean_names() %>%
  mutate(
    babysex = factor(babysex), 
    frace = factor(frace), 
    malform = factor(malform), 
    mrace = factor(mrace)
    )
# check for missing data
baby_df %>%  summarise(na_count = sum(is.na(.))) #no missing value
```

Propose a regression model for birthweight. 

Do step-wise model selection based on AIC.
```{r P2model}
# step-wise model selection based on AIC
step_model = lm(bwt ~ ., data = baby_df) %>%
  stepAIC(direction = "both", trace = F) %>% 
  broom::tidy()

step_model
```

Based on the result, the proposed model is: 
$$bwt = \beta_0 + \beta_1* babysex2 + \beta_2*bhead + \beta_3*blength + \beta_4*delwt + \beta_5*fincome + \beta_6*gaweeks + \beta_7*mheight + \beta_8*mrace2 + \beta_9*mrace3 + \beta_{10}*mrace4  + \beta_{11}*parity + \beta_{12}*ppwt + \beta_{13}*smoken$$

Show a plot of model residuals against fitted values
```{r P2plot}
#proposed model
baby_fit = lm(bwt ~ babysex + bhead + blength + delwt + fincome + gaweeks + mheight + mrace + parity + ppwt + smoken, data = baby_df)
#plot  
baby_df %>% 
  add_predictions(baby_fit) %>% 
  add_residuals(baby_fit) %>% 
  ggplot(aes(y = resid, x = pred)) + 
  geom_point(alpha = .2) + 
  labs(
    title = "Plot of model residuals vs. fitted values",
    x = "Fitted Values",
    y = "Residuals"
  ) # Residual seems not random
```

Comparison:

* One using length at birth and gestational age as predictors (main effects only)

* One using head circumference, length, sex, and all interactions (including the three-way interaction) between these
Make this comparison in terms of the cross-validated prediction error; use crossv_mc and functions in purrr as appropriate.

```{r P2comparison, warnings=FALSE}
#split data for cv
set.seed(0)
cv_df = crossv_mc(baby_df, 100) %>% 
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble)
  )

# calculate rmse
rmse = 
  cv_df %>% 
  mutate(
    proposed_model = map(.x = train, ~lm(bwt ~ babysex + bhead + blength + delwt + fincome + gaweeks + mheight + mrace + parity + ppwt + smoken, data = .x)),
    main_model = map(.x = train, ~lm(bwt ~ blength + gaweeks, data = .x)),
    interact_model = map(.x = train, ~lm(bwt ~ bhead:blength:babysex, data = .x))
  ) %>% 
  mutate(
    rmse_proposed = map2_dbl(.x = proposed_model, .y = test, ~rmse(model = .x, data = .y)),
    rmse_main = map2_dbl(.x = main_model, .y = test, ~rmse(model = .x, data = .y)),
    rmse_intereact = map2_dbl(.x = interact_model, .y = test, ~rmse(model = .x, data = .y))) %>% 
  dplyr::select(starts_with("rmse")) %>% 
  map(mean)

rmse
```

The proposed model has lowest cross-validated prediction error so it's the best among the three, the model using length at birth and gestational age as predictors (main effects only) has the largest cross-validated prediction error, so it's the worst.

# Problem 3

```{r data, message=FALSE}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  dplyr::select(name, id, everything())
```

```{r P3bootstrap}
# bootstrap
set.seed(1)
bootstrap_result = 
  weather_df %>% 
  bootstrap(5000, id = "strap_number") %>% 
  mutate(
    models = map(.x = strap, ~lm(tmax ~ tmin, data = .x)), 
    r_squared = map(models, broom::glance),
    results = map(models, broom::tidy)
  )
# get estimates 
bootstrap_est = bootstrap_result %>% 
  dplyr::select(strap_number, r_squared, results) %>% 
  unnest(r_squared) %>% 
  dplyr::select(strap_number, r.squared, results) %>% 
  unnest(results) %>% 
  janitor::clean_names() %>%  
  dplyr::select(strap_number, r_squared, term, estimate) %>% 
  pivot_wider(
    names_from = term, 
    values_from = estimate
  ) %>% 
  rename(beta_0 = `(Intercept)`, beta_1 = tmin) %>% 
  mutate(log_beta0beta1 = log(beta_0 * beta_1)) %>% 
  dplyr::select(-starts_with("beta_"))

```

Plot the distribution of estimates.
```{r P3plot1}
# distribution of r_squared.
r2_dist = bootstrap_est %>% 
  ggplot(aes(x = r_squared)) + 
  geom_density() + 
  labs(
    title = "Distribution of r^2",
    subtitle = "based on 5000 bootstrap samples", 
    x = "Estimates of r^2")

# distribution of log(beta_0*beta_1)
log_dist = 
  bootstrap_est %>% 
  ggplot(aes(x = log_beta0beta1)) + 
  geom_density() + 
  labs(
    title = "Distribution of log(beta_0 beta_1)",
    subtitle = "based on 5000 bootstrap samples", 
    x = "log(beta_0 beta_1)")
r2_dist + log_dist
```

Both estimates has bell shape distribution curve, their empirical distribution seems to be normal distribution. For $\hat r^2$, it has sample mean = `r mean(bootstrap_est$r_squared)` and standard deviation = `r sd(bootstrap_est$r_squared)`. For $\log (\hat \beta_0 * \hat \beta_1$, it has sample mean = `r mean(bootstrap_est$log_beta0beta1)` and standard deviation = `r sd(bootstrap_est$log_beta0beta1)`.

Calculate CI

* 95% CI for $\hat r^2$ is [`r quantile(bootstrap_est$r_squared, 0.025)`,`r quantile(bootstrap_est$r_squared, 0.975)`].

* 95% CI for $\log (\hat \beta_0 * \hat \beta_1$ is [`r quantile(bootstrap_est$log_beta0beta1, 0.025)`,`r quantile(bootstrap_est$log_beta0beta1, 0.975)`].
